Distributed Topology Discovery in Self-Assembled Nano Networks

### 2014-02-12 trunk/PAPER/paper.tex
Synced to after-conferences updates
Fixed DiSR word

\documentclass[final,journal,letterpaper]{IEEEtran}
%\IEEEoverridecommandlockouts

@@

\usepackage{listings}
\usepackage{listings}
\lstset{
   language=C,
   basicstyle=\small,
   keywordstyle=\bfseries,
   identifierstyle=\ttfamily,
   stringstyle=\ttfamily,
   numbers=left,
   numberstyle=\tiny,
   stepnumber=1,
   numbersep=-5pt,
   showstringspaces=false
%   frame=single %trbl%
}

@@

\newcommand{\etal}{\emph{et al.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\etc}{\emph{etc.}}
\renewcommand{\baselinestretch}{0.97}\normalsize
%------------------------------------------------------------------------------

@@

\title{A First Effort for a Distributed Segment-based Approach on Self-Assembled Nano Networks}

@@

\begin{abstract}
In this paper we present DiSR, a first effort for a distributed
segment-based approach to routing and defect mapping in a nano-scale,
topology agnostic scenario based on DNA self-assembly. The main aim is
exploiting the already-proven qualities of segment-based routing
without neither requiring a topology graph as input, nor needing a
centralized algorithm to configure network paths.  After introducing
the conceptual elements and the execution model of DiSR, we show how
the opensource Nanoxim platform has been used to evaluate the proposed
approach in the process of discovering irregular network topology
while establishing network segments.  Results show how DiSR still
preserves some important properties (coverage, defect tolerance,
scalability)  while avoiding centralized tree-based broadcasting and
resource hungry solutions such as virtual channels and hardware
redundancy. Finally, we analyzed a first, not yet optimised gate-level
hardware implementation of the required control logic and storage for
DiSR, demonstrating a relatively acceptable impact ranging from 10 to
about 20\% of the budget of transistors available for each node.
\end{abstract}

@@

\begin{IEEEkeywords}
Nanotechnology, DNA, Self-assembly, Routing
\end{IEEEkeywords}
%------------------------------------------------------------------------------

@@

\section{Conclusions}
In this work we presented DiSR, an initial attempt of porting a segment based
approach to distributed self-assembled nanoscale scenario. We
demonstrated how DiSR can accomplish the aim of finding a segment
coverage of the network without requiring any centralized approach
that would request a graph topology as input. A draft hardware
implementation has been presented to evaluate the impact on the limited
node size typical of the assumed scenario. Future works will focus on
developing self tuning of DiSR to match a high coverage levels and the
detailed low level hardware implementation on
DNA grid using the appropriate nano devices models.

>>>>

\documentclass[final,journal]{IEEEtran}
%\IEEEoverridecommandlockouts

@@

\usepackage{listings}
\lstset{
   language=C,
   basicstyle=\small,
   keywordstyle=\bfseries,
   identifierstyle=\ttfamily,
   stringstyle=\ttfamily,
   numbers=left,
   numberstyle=\tiny,
   stepnumber=1,
   numbersep=-5pt,
   showstringspaces=false
%   frame=single %trbl%
}

@@

\newcommand{\etal}{\emph{et al.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\etc}{\emph{etc.}}
\newcommand{\disr}{{\sf DiSR}}
%\renewcommand{\baselinestretch}{0.97}\normalsize
%------------------------------------------------------------------------------

@@

\title{Distributed Topology Discovery in Self-Assembled Nano Networks}

@@

\begin{abstract}
In this paper we present \disr{}, a first effort for a distributed
segment-based approach to routing and defect mapping in a nano-scale,
topology agnostic scenario based on DNA self-assembly. The main aim is
exploiting the already-proven qualities of segment-based routing
without neither requiring a topology graph as input, nor needing a
centralized algorithm to configure network paths.  After introducing
the conceptual elements and the execution model of \disr{}, we show how
the opensource Nanoxim platform has been used to evaluate the proposed
approach in the process of discovering irregular network topology
while establishing network segments.  Results show how \disr{} still
preserves some important properties (coverage, defect tolerance,
scalability)  while avoiding centralized tree-based broadcasting and
resource hungry solutions such as virtual channels and hardware
redundancy. Finally, we analyzed a first, not yet optimised gate-level
hardware implementation of the required control logic and storage for
\disr{}, demonstrating a relatively acceptable impact ranging from 10 to
about 20\% of the budget of transistors available for each node.
\end{abstract}

@@

\begin{IEEEkeywords}
Nanotechnology, DNA, Self-assembly, Routing, Deadlock
\end{IEEEkeywords}
%------------------------------------------------------------------------------

@@

\section{Conclusions}
In this work we presented \disr{}, an initial attempt of porting a segment based
approach to distributed self-assembled nanoscale scenario. We
demonstrated how \disr{} can accomplish the aim of finding a segment
coverage of the network without requiring any centralized approach
that would request a graph topology as input. A draft hardware
implementation has been presented to evaluate the impact on the limited
node size typical of the assumed scenario. Future works will focus on
developing self tuning of \disr{} to match a high coverage levels and the
detailed low level hardware implementation on
DNA grid using the appropriate nano devices models.
